\bf $\mathsf{BATE}$: Boosting Bandwidth Availability Over Inter-DC WAN

### 2021-01-26 paper.tex
20210126

@@

However, service providers have to refund credits to users if their bandwidth availability targets according the agreed SLAs are violated (see $\S$\ref{background}), both for users affected \textit{directly} by the failure and for users \textit{collaterally} affected by the recovery procedure. 
Our failure recovery scheme takes this economic factor into account in the way as follows.
%
%
%
\begin{figure}[t]
\centering
\subfigure[Original allocation]{
\includegraphics[width=0.23\textwidth]{fig/recovery-1.pdf}}
\subfigure[Backup allocation]{
\includegraphics[width=0.23\textwidth]{fig/recovery-2.pdf}}
%\caption{There are two services from DC1 to DC4 and link capacity is 1 everywhere. (a) shows the original TE allocation. (b) shows the backup allocation result when assuming link DC2 $\to$ DC4 is broken.  }
\caption{Bandwidth allocation for DC2$\to$DC4 failure}
\label{recovery}
\end{figure}
%\begin{equation}
%\small
%\begin{aligned} \label{BATE-recovery}
% &maximize  \sum_{i\in I_a} \sum_{\mathbf{z}\in \mathbf{z}}B_d^{\mathbf{z}}\times p_{\mathbf{z}}\\
%&\begin{array}{r@{\quad}r@{}l@{\quad}l}
%s.t.
%\begin{cases}
%\sum_{i\in I_a}\sum_{k\in K}\sum_{t\in Q_{h}} f'_{ikt}u_t^e+ \sum_{i\in I_a}\sum_{k\in K}\sum_{t'\in Q_{h}} f''_{ikt'}L_{t'e} \le c_e, &\text{$\forall e \in E \setminus e' $.}\\
%R_{dk}^{\mathbf{z}}=\frac{\sum_{k\in K}\sum_{t\in T_{k}}f_{d}^tv_t^{\mathbf{z}} }{\mathbf{b}^k_d} , &\text{$\forall  d \in \hat{D}, \mathbf{z}\in \mathbf{z},  k \in K$.}\\
%R_{dk}^{\mathbf{z}}>=B_d^{\mathbf{z}},&{\forall d \in \hat{D}, \mathbf{z} \in Z, k\in K.} \\
%\sum_{\mathbf{z}\in \mathbf{z}}B_d^{\mathbf{z}}\times p_{\mathbf{z}} \ge \beta_{\gamma_{i}},&{\forall d \in \hat{D}} .\\
% \sum_{t\in T_{k}} f_{d}^t \le \mathbf{b}^k_d, &{  \forall d \in \hat{D}, k \in K}.\\
%f_{d}^t \ge 0,&{\forall d \in \hat{D} , \forall k\in K,\forall t\in T_{k}}.\\
%\end{cases}\\
%\end{array}
%\end{aligned}
%\end{equation}

@@

\begin{figure}
\begin{center}
\includegraphics [width=0.8\columnwidth] {fig/inter-DC-WAN-V3.pdf}
\caption{System architecture of $\mathsf{BATE}$}
\label{pic-overview}
\end{center}
\end{figure}

@@

 \begin{figure}[t]
\begin{center}
\includegraphics [width=0.68\columnwidth] {fig/testbed.pdf}
\caption{Testbed topology with failure probabilities}
\label{testbed}
\end{center}
\end{figure}
%
%
% \begin{figure}
%\begin{center}
%\includegraphics [width=0.8\columnwidth] {fig/evaluation/testbed-admit.pdf}
%\caption{Admission control comparison.}
%\label{admission-control2}
%\end{center}
%\end{figure}
%
%
%
%\begin{figure}
%\centering
%\subfigure[Availability satisfaction]{
%\includegraphics[width=0.23\textwidth]{fig/evaluation/fake-testbed-target.pdf}}
%\subfigure[Admission time]{
%\includegraphics[width=0.23\textwidth]{fig/evaluation/testbed-public-2.pdf}}
%\caption{Traffic scheduling comparison.}
%\label{testbed-traffic-scheduling}
%\end{figure}

\begin{figure*}
\centering
\subfigure[Admission control]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/testbed-admit.pdf}}
\subfigure[Traffic scheduling]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/fake-testbed-target.pdf}}
\subfigure[Profit loss after failures]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/testbet-loss2.pdf}}
\subfigure[Overall profit gain]{
\includegraphics[width=0.23\textwidth]{fig/evaluation/overall-profit.pdf}}
\caption{Testbed evaluation with Poisson demand arrivals}
\label{e2}
\end{figure*}

@@

(2) $\mathsf{BATE}$ achieves a good tradeoff between efficiency and optimality. 
Compared with the optimal solutions, (i) our admission control algorithm can speed up the admission procedure by 30$\times$ at the expense of less than 4\% false rejections, 
(ii) our pruning-augmented scheduling algorithm runs $10^2 \sim 10^4 \times$ faster while wasting only 6\% total bandwidth, 
and (iii) our greedy failure recovery algorithm can reduce the reaction time by xx$\times$, 
where the profit loss is only around 10\%.

(3) $\mathsf{BATE}$ has a stable performance across differnet network topologies, link characteristics, 
demand matrices and routing schemes.

@@

\begin{figure*}[t]
\centering
%\begin{tabular}{c}
%\includegraphics[width=0.7\textwidth]{fig/evaluation/legend.pdf}
%\end{tabular}
%\vfill
\subfigure[Rejection ratio]{
\includegraphics[width=0.32\textwidth]{fig/evaluation/sim-admit.pdf}}
\subfigure[Link utilization]{
\includegraphics[width=0.32\textwidth]{fig/evaluation/link-utilization.pdf}}
\subfigure[Admission delay]{
\includegraphics[width=0.32\textwidth]{fig/evaluation/admission-control-time.pdf}}
\caption{Admission control results in simulations}
\label{availability_fig1}
\end{figure*}

@@

\begin{figure}[t]
\centering
\subfigure[$\mathsf{BATE}$ v.s. other TE algorithms]{
\includegraphics[width=0.45\textwidth]{fig/evaluation/no-fixed.pdf}}
\subfigure[augmented with \textit{fixed} admission control]{
\includegraphics[width=0.45\textwidth]{fig/evaluation/fixed-shuduling.pdf}}
\caption{BA satisfaction results under simulations}
\label{scheduling-benefit}
\end{figure}

@@

\textbf{Evaluation results.}
\begin{figure}[t]
\begin{center}
\includegraphics [width=0.9\columnwidth] {fig/evaluation/sim-monney.pdf}
\caption{Profit gain after failures}
\label{sim-profit}
\end{center}
\end{figure}
Figure \ref{availability_fig1} compares, under different demand arrival rates, 
the admission results of $\mathsf{BATE}$  against  
the optimal strategy and the \textit{fixed} one, i.e., step (1) in $\mathsf{BATE}$. 
Figure \ref{availability_fig1}(a) shows that, $\mathsf{BATE}$ falsely rejects at most 4\% demands (using the optimal solution as a baseline), but accepts up to 50\% more demands with a much smaller variance than Fixed. 
It can also utilize at least 10\% higher bandwith than Fixed, as shown in Figure \ref{availability_fig1}(b). 
We also qualify their efficiency by measuring the admission control delay, and Figure \ref{availability_fig1}(c) demonstrates that, $\mathsf{BATE}$ runs at least 30$\times$ faster than directly solving the MILP optimization problem, and always finishes within 1 second. 
%
%\begin{figure}[t]
%\begin{center}
%\includegraphics [width=0.8\columnwidth] {fig/evaluation/sim-monney.pdf}
%\caption{Profit gain after failures}
%\label{sim-profit}
%\end{center}
%\end{figure}

@@

\iffalse
%We write down the bandwidth loss of each scenario for each demand and each scenario's corresponding probability.
The sum of scenario probability where demand is fully satisfied reflects the \textit{achieved availability}.
%If a demand's , then the availability defined in SLA is \textit{satisfaction}.
The term \textit{satisfaction percentage} refers to the fraction of total arrival demands whose achieved availability are higher than their availability targets throughout duration.
Figure \ref{scheduling-benefit}(a) demonstrates that $\mathsf{BATE}$ can even make up to 40\% more demands satisfy SLA availability.
%Demands SLA violation of  $\mathsf{BATE}$ mainly comes from admission control rejection.
%The reason for this is that $\mathsf{BATE}$ adopts admission control and it considers the diverse availability targets of different bandwidth demands.
$\mathsf{BATE}$ can make demands with stringent availability requirements pass links with high reliability, therefore, their availability targets can be guaranteed, but other schemes are unable differentiate demands.
To show this benefit, we adopt \textit{Fixed} admission control for each traffic scheduling algorithm, then Figure \ref{scheduling-benefit}(b) shows $\mathsf{BATE}$ performs at least 10\% better than other algorithms under the \textit{Fixed} admission control method.
\fi

Figure \ref{sim-profit} shows the average profit after failures occur in the network.
Due to its considration of pricing and refunding,  
$\mathsf{BATE}$ is able to retain 10\%$\sim$20\% more profit than the other algorithms.
\footnote{Our preliminary results show $\mathsf{BATE}$ will perform even better than the others under more complicated multi-stage SLAs, especially when the refunding ratio $\mu=1$ under low satisfaction.}

>>>>

\setlength{\textfloatsep}{3.8pt}

@@

However, service providers have to refund credits to users if their bandwidth availability targets according the agreed SLAs are violated (see $\S$\ref{background}), both for users affected \textit{directly} by the failure and for users \textit{collaterally} affected by the recovery procedure. 
Our failure recovery scheme takes this economic factor into account in the way as follows.
%
%
%
\begin{figure}[t]
\centering
\subfigure[Original allocation]{
\includegraphics[width=0.2\textwidth]{fig/recovery-1.pdf}}
\subfigure[Backup allocation]{
\includegraphics[width=0.2\textwidth]{fig/recovery-2.pdf}}
%\caption{There are two services from DC1 to DC4 and link capacity is 1 everywhere. (a) shows the original TE allocation. (b) shows the backup allocation result when assuming link DC2 $\to$ DC4 is broken.  }
\caption{Bandwidth allocation for DC2$\to$DC4 failure}
\label{recovery}
\end{figure}
%\begin{equation}
%\small
%\begin{aligned} \label{BATE-recovery}
% &maximize  \sum_{i\in I_a} \sum_{\mathbf{z}\in \mathbf{z}}B_d^{\mathbf{z}}\times p_{\mathbf{z}}\\
%&\begin{array}{r@{\quad}r@{}l@{\quad}l}
%s.t.
%\begin{cases}
%\sum_{i\in I_a}\sum_{k\in K}\sum_{t\in Q_{h}} f'_{ikt}u_t^e+ \sum_{i\in I_a}\sum_{k\in K}\sum_{t'\in Q_{h}} f''_{ikt'}L_{t'e} \le c_e, &\text{$\forall e \in E \setminus e' $.}\\
%R_{dk}^{\mathbf{z}}=\frac{\sum_{k\in K}\sum_{t\in T_{k}}f_{d}^tv_t^{\mathbf{z}} }{\mathbf{b}^k_d} , &\text{$\forall  d \in \hat{D}, \mathbf{z}\in \mathbf{z},  k \in K$.}\\
%R_{dk}^{\mathbf{z}}>=B_d^{\mathbf{z}},&{\forall d \in \hat{D}, \mathbf{z} \in Z, k\in K.} \\
%\sum_{\mathbf{z}\in \mathbf{z}}B_d^{\mathbf{z}}\times p_{\mathbf{z}} \ge \beta_{\gamma_{i}},&{\forall d \in \hat{D}} .\\
% \sum_{t\in T_{k}} f_{d}^t \le \mathbf{b}^k_d, &{  \forall d \in \hat{D}, k \in K}.\\
%f_{d}^t \ge 0,&{\forall d \in \hat{D} , \forall k\in K,\forall t\in T_{k}}.\\
%\end{cases}\\
%\end{array}
%\end{aligned}
%\end{equation}

@@

\begin{figure}
\begin{center}
\includegraphics [width=0.7\columnwidth] {fig/inter-DC-WAN-V3.pdf}
\caption{System architecture of $\mathsf{BATE}$}
\label{pic-overview}
\end{center}
\end{figure}

@@

 \begin{figure}[t]
\begin{center}
\includegraphics [width=0.6\columnwidth] {fig/testbed.pdf}
\caption{Testbed topology with failure probabilities}
\label{testbed}
\end{center}
\end{figure}
%
%
% \begin{figure}
%\begin{center}
%\includegraphics [width=0.8\columnwidth] {fig/evaluation/testbed-admit.pdf}
%\caption{Admission control comparison.}
%\label{admission-control2}
%\end{center}
%\end{figure}
%
%
%
%\begin{figure}
%\centering
%\subfigure[Availability satisfaction]{
%\includegraphics[width=0.23\textwidth]{fig/evaluation/fake-testbed-target.pdf}}
%\subfigure[Admission time]{
%\includegraphics[width=0.23\textwidth]{fig/evaluation/testbed-public-2.pdf}}
%\caption{Traffic scheduling comparison.}
%\label{testbed-traffic-scheduling}
%\end{figure}

\begin{figure*}
\centering
\subfigure[Admission control]{
\includegraphics[width=0.24\textwidth]{fig/evaluation/testbed-admit.pdf}}
\subfigure[Traffic scheduling]{
\includegraphics[width=0.24\textwidth]{fig/evaluation/fake-testbed-target.pdf}}
\subfigure[Profit loss after failures]{
\includegraphics[width=0.24\textwidth]{fig/evaluation/testbet-loss2.pdf}}
\subfigure[Overall profit gain]{
\includegraphics[width=0.24\textwidth]{fig/evaluation/overall-profit.pdf}}
\caption{Testbed evaluation with Poisson demand arrivals}
\label{e2}
\end{figure*}

@@

(2) $\mathsf{BATE}$ achieves a good tradeoff between efficiency and optimality. 
Compared with the optimal solutions, (i) our admission control algorithm can speed up the admission procedure by 30$\times$ at the expense of less than 4\% false rejections, 
(ii) our pruning-augmented scheduling algorithm runs $10^2 \sim 10^4 \times$ faster while wasting only 6\% total bandwidth, 
and (iii) our greedy failure recovery algorithm can reduce the reaction time by xx$\times$, 
where profit loss is only around 10\%.

(3) $\mathsf{BATE}$ has a stable performance across different network topologies, 
demand matrices and routing schemes.

@@

\begin{figure*}[t]
\centering
%\begin{tabular}{c}
%\includegraphics[width=0.7\textwidth]{fig/evaluation/legend.pdf}
%\end{tabular}
%\vfill
\subfigure[Rejection ratio]{
\includegraphics[width=0.3\textwidth]{fig/evaluation/sim-admit.pdf}}
\subfigure[Link utilization]{
\includegraphics[width=0.3\textwidth]{fig/evaluation/link-utilization.pdf}}
\subfigure[Admission delay]{
\includegraphics[width=0.3\textwidth]{fig/evaluation/admission-control-time.pdf}}
\caption{Admission control results in simulations}
\label{availability_fig1}
\end{figure*}

@@

\begin{figure}[t]
\centering
\subfigure[$\mathsf{BATE}$ v.s. other TE algorithms]{
\includegraphics[width=0.4\textwidth]{fig/evaluation/no-fixed.pdf}}
\subfigure[augmented with \textit{fixed} admission control]{
\includegraphics[width=0.4\textwidth]{fig/evaluation/fixed-shuduling.pdf}}
\caption{BA satisfaction results under simulations}
\label{scheduling-benefit}
\end{figure}

@@

\textbf{Evaluation results.}

Figure \ref{availability_fig1} compares, under different demand arrival rates, 
the admission results of $\mathsf{BATE}$  against  
the optimal strategy and the \textit{fixed} one, i.e., step (1) in $\mathsf{BATE}$. 
Figure \ref{availability_fig1}(a) shows that, $\mathsf{BATE}$ falsely rejects at most 4\% demands (using the optimal solution as a baseline), but accepts up to 50\% more demands with a much smaller variance than Fixed. 
It can also utilize at least 10\% higher bandwith than Fixed, as shown in Figure \ref{availability_fig1}(b). 
We also qualify their efficiency by measuring the admission control delay, and Figure \ref{availability_fig1}(c) demonstrates that, $\mathsf{BATE}$ runs at least 30$\times$ faster than directly solving the MILP optimization problem, and always finishes within 1 second. 
%
%\begin{figure}[t]
%\begin{center}
%\includegraphics [width=0.8\columnwidth] {fig/evaluation/sim-monney.pdf}
%\caption{Profit gain after failures}
%\label{sim-profit}
%\end{center}
%\end{figure}

@@

\iffalse
%We write down the bandwidth loss of each scenario for each demand and each scenario's corresponding probability.
The sum of scenario probability where demand is fully satisfied reflects the \textit{achieved availability}.
%If a demand's , then the availability defined in SLA is \textit{satisfaction}.
The term \textit{satisfaction percentage} refers to the fraction of total arrival demands whose achieved availability are higher than their availability targets throughout duration.
Figure \ref{scheduling-benefit}(a) demonstrates that $\mathsf{BATE}$ can even make up to 40\% more demands satisfy SLA availability.
%Demands SLA violation of  $\mathsf{BATE}$ mainly comes from admission control rejection.
%The reason for this is that $\mathsf{BATE}$ adopts admission control and it considers the diverse availability targets of different bandwidth demands.
$\mathsf{BATE}$ can make demands with stringent availability requirements pass links with high reliability, therefore, their availability targets can be guaranteed, but other schemes are unable differentiate demands.
To show this benefit, we adopt \textit{Fixed} admission control for each traffic scheduling algorithm, then Figure \ref{scheduling-benefit}(b) shows $\mathsf{BATE}$ performs at least 10\% better than other algorithms under the \textit{Fixed} admission control method.
\fi
\begin{figure}[t]
\begin{center}
\includegraphics [width=0.8\columnwidth] {fig/evaluation/sim-monney.pdf}
\caption{Profit gain after failures}
\label{sim-profit}
\end{center}
\end{figure}
Figure \ref{sim-profit} shows the average profit after failures occur in the network.
Due to its considration of pricing and refunding,  
$\mathsf{BATE}$ is able to retain 10\%$\sim$20\% more profit than the other algorithms.
\footnote{Our preliminary results show $\mathsf{BATE}$ will perform even better than the others under more complicated multi-stage SLAs, especially when the refunding ratio $\mu=1$ under low satisfaction.}
